### 2020-04-19 tex/ResponseLetterR120200418.tex

\documentclass[a4paper]{article}
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=2.0cm,bottom=2.0cm}
\usepackage{booktabs}
\usepackage{color}
\usepackage{threeparttable}
\usepackage{array}
\usepackage{float}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{subfigure}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath,amssymb,amsfonts,amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{fancyhdr}
\usepackage{bm}
\usepackage{url}
\usepackage{enumerate}

\usepackage{amsopn}
%\graphicspath{{JFI/IPWeightingFun/}}

\newtheorem{thm}{Theorem}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}{Definition}

\makeatletter
\long\def\@makecaption#1#2{%
\vskip\abovecaptionskip
\sbox\@tempboxa{#1.\quad #2}%
\ifdim \wd\@tempboxa >\hsize
 #1.\quad #2\par
\else
 \global \@minipagefalse
 \hb@xt@\hsize{\hfil\box\@tempboxa\hfil}%
\fi
\vskip\belowcaptionskip}
\makeatother

%\renewcommand{figurename}{\textbf{Fig.}}
\renewcommand\figurename{Fig.}

\fancypagestyle{plain}{%
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{\bfseries \thepage} % except the center
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}}
\linespread{1.2}
\begin{document}
\pagestyle{plain}
\title{The thorough and point-by-point description of the changes implemented (Revision 1)}
\maketitle

Thanks for the comments on our manuscript ``Receding horizon $H_{\infty}$ control for nonlinear systems with tensor product model transformation''.  We would like to gratefully thank the reviewer for his or her valuable recommendation on this paper. We have rechecked the paper and references carefully. \textcolor[rgb]{1,0,0}{The revised parts are shown in bold type in revised paper}. The following responses have been prepared to address all of the reviewers' comments in a point-by-point fashion.
\vskip 0.3cm

\textbf{Reviewer(s)' Comments to Author:}

\textbf{Handling AE:} The paper is well written and organized, and the main results have some originality. I think the addressed problem is interesting and the paper contains acceptable materials. So, I recommend acceptance of the paper for Oral presentation in CCC 2020.

------------------------------------------------------------------------------------------------

\textit{\textbf{Reviewer \#1:} In this paper, a tensor product-based control method is proposed for external non-linear disturbances. Based on the TP model, the knowledge of multicellular systems is used to transform a linear variable parameter model into a linear parameter weighted combination. A set of weighted matrix inequality conditions is proposed. }

\textit{Using the conditions of linear matrix inequality and based on the PDC method, it is obtained that the system gradually meets $H_{\infty}$ performance under external disturbances. }

\textit{Finally, three examples show that the $H_{\infty}$ controller using the tensor product model has stable control, so that all states eventually approach the origin. However, there are some comments as follows:}

\textbf{Problem 1:} \textit{In the process of demonstrating that the derivative of the performance index is less than 0, reducing the conservativeness of the system with the convenience of calculation, it need be explained clearly.}

\textbf{Answer 1} Thanks for the valuable comments.

\textbf{Problem 2:} \textit{Three examples verify the stability of the rolling time-domain $H_{\infty}$ controller for a nonlinear system based on the tensor product model transformation. If it can be compared with other methods of controllers to highlight the superiority of the tensor product model transformation .}

\textbf{Answer 2} Thanks for the valuable comments.

------------------------------------------------------------------------------------------------

\textit{\textbf{Reviewer \#2:} The paper studied the problem of receding horizon $H_{\infty}$ control for nonlinear systems with tensor product model transformation. }

\textit{A new set of matrix inequality conditions on the terminal weighting matrix is proposed for TP modeled nonlinear systems wherein non-increasing monotonicity of the optimal cost is guaranteed. The paper is well written. I recommend this paper for publication,however, the following comments should be solved in the revision: }

Many thanks for the comments from reviewer 2.

\textbf{Problem 1:} \textit{In Section III, what is the pratical background of the novel finite horizon cost function given by (4), the authors should clarify it.}

\textbf{Answer 1} Thanks for the valuable comments.

\textbf{Problem 2:} \textit{What is the methods used in the study of H infinity performance? Some comparisons should be made between the existing result such as Information Sciences, 2020, 512: 327-337.}

[1] Optimal performance of LTI systems over power constrained erasure channels. Information Sciences, 2020. 512: p. 327-337.

\textbf{Answer 2} Thanks for the valuable comments.

------------------------------------------------------------------------------------------------

\textit{\textbf{Reviewer \#3:}  In this paper, a novel tensor-product based receding horizon $H_{\infty}$ control (TPRHHC) method for nonlinear systems with external disturbance is proposed and linear matrix inequalities are given to show the stability of the system. The following comments are provided to enhance the quality of this paper as follows:}

Many thanks for the comments from reviewer 3.

\textbf{Problem 1:} \textit{The introduction lacks logicality and the necessity of doing research about TPRHHC is not clear.}

\textbf{Answer 1} Thanks for the valuable comments.

\textbf{Problem 2:} \textit{Please elaborate the technology tensor product and what are the pros and cons of this technology?}

\textbf{Answer 2} Thanks for the valuable comments.

\textbf{Problem 3:} \textit{The English writing is not formal and correct enough. }

\textbf{Answer 3} Thanks for the valuable comments.

\textbf{Problem 4:} \textit{ In the simulation, the comparison of TPRHHC and RHC should be given to show the advantages of the proposed control scheme.}

\textbf{Answer 4} Thanks for the valuable comments.

\textbf{Problem 5:} \textit{Why do the authors choose these three special systems to verify the proposed control scheme? These three examples may not complex enough.}

\textbf{Answer 5} Thanks for the valuable comments.

------------------------------------------------------------------------------------------------

\textit{\textbf{Reviewer \#4:} Some problems that I concerned are given in the following.}

Many thanks for the comments from reviewer 4.

\textbf{Problem 1:} \textit{The last paragraph on the first page had better be divided into two paragraphs.}

\textbf{Answer 1} Thanks for your valuable comments.

\textbf{Problem 2:} \textit{Page 2,$S(p(t)) \in \operatorname{conv}\left\{S_{1}, S_{2}, \cdots,S_{r}\right\}\left\{\sum_{i=1}^{r} w_{i} S_{i}: w_{i} \leq 0, \sum_{i=1}^{r} w_{i}=1\right\}$,can you sure $\omega_i \leq 0$?}

\textbf{Answer 2} Thanks for your valuable comments.

\textbf{Problem 3:} \textit{Page 2,$u=\sum_{i=1}^{r} K_i x$,Why the expression of the controller has nothing to do with fuzzy member functions?}

\textbf{Answer 3} Thanks for your valuable comments.

\textbf{Problem 4:} \textit{There exist some grammar mistakes and typos in this paper. Some of them are listed as follows:}

\begin{itemize}
\item  \textit {page 1: a) the main feature of RHC is its performance index has a moving initial time and a moving terminal time.}

    \textit{ b) In [10], a distributed receding horizon control method of a vehicle platoon with nonlinear dynamics is designed a novel optimization problem and detailed distributed;}

    \textit{c) moreover, it handles atypical measurement noise;}

\item \textit{Page 2: In Remark1, $r$ should be $i$;}
\item \textit{Page 4: First, Before the main theorem we need the the following;}
\item \textit{Page 5: $\dot{x}(t))$}
\item \textit{page 6: $[x(t), y(t), z(t)]^{T} \in R^{3}$}
\end{itemize}

\textbf{Answer 4} Thanks for your valuable comments.

------------------------------------------------------------------------------------------------
\end{document}

### 2020-04-19 tex/chapter3.tex
20200416人工智能教案
20200417人工智能教案
20200419人工智能教案

      (5) \textcolor[rgb]{0,0,1}{拒取式}           $ \neg Q,  P\rightarrow Q \Rightarrow  P$.

@@

这四种二元归结式都是子句$C_1$和$C_2$的二元归结式, 记为$C_{12}$.
\end{mydef}
%%%%%%%-----------------------------------------------
\begin{example}
    设$C_1=P(y)\vee P(f(x))\vee Q(g(x)), C_2 =\neg P(f(g(a)))\vee Q(b)$, 求$C_{12}$.
\end{example}
%%%%%%%----------------------------------------
\begin{result}
    对$C_1$取最一般合一$\sigma =\{f(x)/y\}$, 得$C_1$的因子
\begin{align}
    C_1\sigma =P(f(x))\vee Q(g(x)),
\end{align}
对$C_1$的因子和$C_2$归结(合一$\sigma=\{g(a)/x\}$), 可得到$C_1$和$C_2$的二元归结式
\begin{align}
    C_{12}=Q(g(g(a)))\vee Q(b).
\end{align}
\end{result}
%%%%%%%-----------------------------------------
\begin{remark}
    对谓词逻辑, 定理3.2仍然适用, 即归结式$C_{12}$是其亲本子句$C_1$和$C_2$的逻辑结论. 用归结式取代它在子句集$S$中的亲本子句, 所得到的子句集仍然保持着原子句集$S$的不可满足性.
此外, 对谓词逻辑定理3.3也仍然适用, 即从不可满足的意义上说, 一阶谓词逻辑的归结原理完备.
\end{remark}
%%%%%%%--------------------------------------
\subsubsection{谓词逻辑的归结反演}
谓词逻辑的归结反演过程与命题逻辑的归结反演过程相比, 其步骤基本相同, 但每步的处理对象不同.
%%%%%%%-----------------------------------------------	
\begin{itemize}
    \item 在步骤(3)化简子句集时, 谓词逻辑需要把由谓词构成的公式集化为子句集;
    \item 在步骤(4)按归结原理进行归结时, 谓词逻辑的归结原理需要考虑两个亲本子句的最一般合一.
\end{itemize}
%%%%%%%-----------------------------------------------
\begin{example}
已知
\begin{align}
 &F:  (\forall x)((\exists  y)(A(x, y)\wedge B(y))\textcolor[rgb]{0,0,1}{\rightarrow} (\exists  y)(C(y)\wedge D(x, y))),\\
 &G: \neg (\exists  x)C(x)\textcolor[rgb]{0,0,1}{\rightarrow} (\forall x)(\forall y)(A(x, y)\rightarrow \neg B(y)).
\end{align}
求证$G$是$F$的逻辑结论.
\end{example}
%%%%%%%----------------------------------------
\begin{proof}
    先把$G$否定, 并放入$F$中, 得到的$\{F, \neg G\}$为
\begin{align}
  \{F, \neg G\}=\{
    &(\forall x)((\exists y)(A(x,y)\wedge B(y))\textcolor[rgb]{0,0,1}{\rightarrow} (\exists y)(C(y)\wedge D(x,y))),\\
    &\neg (\neg (\exists x)C(x)\textcolor[rgb]{0,0,1}{\rightarrow} (\forall  x)(\forall y)(A(x,y)\rightarrow \neg B(y)))\}.
\end{align}

@@

     (8) $\textup{NIL}$, 由(5)和(7)归结, 取合一$\sigma=\{n/k\}$, 因此, $G$是$F$的逻辑结论.
\end{proof}

上述归结过程可用归结树(图\ref{AI32fig16})来表示
 %%%%%%%-----------------------------------------------
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.76\textwidth]{guijieyuanli2019112516.PNG}
%\caption{归结树}
%\label{AI32fig16}
%\end{figure}
%%%%%%%----------------------------------------
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}[font={\sf \small}]
\def \smbwd{2cm}
\def \smbwe{4cm}
\thispagestyle{empty}
%定义流程图的具体形状
\node (ABC0) at (-1,0) [draw, process,minimum width=\smbwd, minimum height=0.5cm] {$\neg \mathbf{A}(\mathbf{x}, \mathbf{y}) \vee \neg \mathbf{B}(\mathbf{y}) \vee \mathbf{C}(\mathbf{f}(\mathbf{x}))$}; % 10
\node (nCz)[draw, process,align=center,right=3cm of Gei,yshift=0cm] {$\neg \mathbf{C}(\mathbf{z})$};                                                                                                    %11
\node (AB0)[draw, process,align=center,below=1.5cm of ABC0,yshift=0cm,xshift=2cm] {$\neg \mathbf{A}(\mathbf{x}, \mathbf{y}) \vee \neg \mathbf{B}(\mathbf{y})$};                                         %20
\draw[thick,-](ABC0)--(AB0)node[left,yshift=1.2cm,xshift=-1.16cm] {$\{f(x)/z\}$};

@@

宽度优先策略的归结树如下:
%%%%%%%-----------------------------------------------
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.76\textwidth]{Gguijieshu2019112520.PNG}
%\caption{广义归结树}
%\label{AI32fig20}
%\end{figure}
%%%%%%%----------------------------------------
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}[font={\sf \small}]
\def \smbwd{2cm}
\def \smbwe{4cm}
\thispagestyle{empty}
%定义流程图的具体形状
\node (ABC0) at (-2,0) [draw, process,minimum width=\smbwd, minimum height=0.5cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\neg \mathbf{I}(x) \vee \mathbf{R}(x)}$};
\node (S)[align=center,left=1cm of ABC0] {$\textcolor[rgb]{0.2,0.6,0.2}{\mathbf{S}}$};
\node (Ia0)[draw, process,align=center,right=1cm of ABC0,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\mathbf{I}(a)}$};
\node (RyLy0)[draw, process,align=center,right=3cm of ABC0,yshift=0cm,xshift=0.6cm] {$\textcolor[rgb]{0,0.0,1}{\neg \mathbf{R}(y) \vee \mathbf{L}(y)}$};
\node (La0)[draw, process,align=center,right=8cm of ABC0,xshift=1cm] {$\textcolor[rgb]{0,0.0,1}{\neg \mathbf{L}(a)}$};
%\draw[thick,->] (Gei.east)->(jiangtao) node[left,yshift=0.25cm,xshift=-1cm] {Receiver};

@@

\node (nI0)[draw, process,align=center,below=1.5cm of Ra1,yshift=0cm,xshift=0.0cm] {$\mathbf{L}(a)$};
\node (S2)[align=center,left=1.5cm of nI0,yshift=0cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\mathbf{S2}}$};
\draw[thick,-](Ra1)--(nI0);
\draw[thick,-](RyLy0)--(nI0);
\node (nLa)[draw, process,align=center,right=1.05cm of nI0,yshift=0cm,xshift=0.5cm] {$\mathbf{L}(a)$};
\draw[thick,-](RanegA)--(nLa);
\draw[thick,-](Ia0)--(nLa);
\node (nLa0)[draw, process,align=center,right=1.cm of nLa,yshift=0cm,xshift=0.5cm] {$\neg\mathbf{I}(a)$};
\draw[thick,-](nRa1)--(nLa0);
\draw[thick,-](ABC0)--(nLa0);
\node (nnnmI0)[draw, process,align=center,right=1.5cm of nLa0,yshift=0cm,xshift=0.5cm] {$\neg\mathbf{I}(a)$};
\draw[thick,-](La0)--(nnnmI0);
\draw[thick,-](RanegA)--(nnnmI0);
\node (nilnil)[draw, process,align=center,right=1.cm of nnnmI0,yshift=0cm,xshift=0.6cm] {\textup{NIL}};
\draw[thick,-](Ra1)--(nilnil);
\draw[thick,-](nRa1)--(nilnil);
\end{tikzpicture}
\end{center}
\caption{广义归结树}
\label{AI32fig20}
\end{figure}
从这个例子可以看出, 宽度优先策略归结出了许多无用的子句, 既浪费事间, 又浪费空间. 但是, 这种策略在当问题有解时保证能找到最短归结路径.
因此, 它是一种完备的归结策略. 宽度优先对复杂问题的归结容易产生组合爆炸, 但对简单问题仍是一种比较好的归结策略.
%%%%%%%-----------------------------------------------
\subsection{支持集策略}
 支持集策略是沃斯(Wos)等人在1965年提出的一种归结策略.
\begin{remark}
    要求每一次参加归结的两个亲本子句中至少应该有一个子句是由目标公式的否定所得到的或它们的后裔.
\end{remark}
 可以证明支持集策略是完备的, 即当子句集为不可满足时, 则由支持集策略一定能够归结出一个空子句.
 也可以把支持集策略看成是在宽度优先策略中引入了某种限制条件, 这种限制条件代表一种启发信息, 因而有较高的效率.
%%%%%%%-----------------------------------------------
\begin{example}
设有如下子句集:
\begin{align}
    S=\{\neg I(x)\vee R(x),  I(a),\neg  R(y)\vee L(y), \neg L(a)\},
\end{align}
其中, $\neg I(x)\vee R(x)$为目标公式的否定. 用支持集策略证明$S$为不可满足.
\end{example}
 %%%%%%%-----------------------------------------------
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.76\textwidth]{Gguijieshu2019112521.PNG}
%\caption{支持集策略}
%\label{AI32fig21}
%\end{figure}
%%%%%%%----------------------------------------
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}[font={\sf \small},scale=0.9]
\def \smbwd{2cm}
\def \smbwe{4cm}
\thispagestyle{empty}
%定义流程图的具体形状
\node (ABC0) at (-2,0) [draw, process,minimum width=\smbwd, minimum height=0.5cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\neg \mathbf{I}(\mathbf{x}) \vee \neg \mathbf{R}(\mathbf{x})}$}; % 10
\node (Ia0)[draw, process,align=center,right=1cm of ABC0,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\mathbf{I}(\mathbf{a})}$};           %12
\node (RyLy0)[draw, process,align=center,right=3cm of ABC0,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\neg\mathbf{R}(\mathbf{y})\vee \mathbf{L}(\mathbf{y})}$};           %132
\node (La0)[draw, process,align=center,right=8cm of ABC0,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\neg \mathbf{L}(\mathbf{a})}$};      %14
%\draw[thick,->] (Gei.east)->(jiangtao) node[left,yshift=0.25cm,xshift=-1cm] {Receiver};

\node (Ra1)[draw, process,align=center,below=2cm of ABC0,yshift=0cm,xshift=-1cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\mathbf{R}(\mathbf{a})}$};        %20
\node (IxLx1)[draw, process,align=center,below=2cm of nCz,yshift=0cm,xshift=-2cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\neg\mathbf{I}(\mathbf{x})\vee \mathbf{L}(\mathbf{x})}$};   %21
\draw[thick,-](ABC0)--(Ra1);
\draw[thick,-](ABC0)--(IxLx1);
\draw[thick,-](Ia0)--(Ra1);
\draw[thick,-](La0)--(Ra1);

\node (La2)[draw, process,align=center,below=2cm of Ra1,yshift=0cm,xshift=1.75cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\mathbf{L}(\mathbf{a})}$};        %30
\node (La21)[draw, process,align=center,right=2cm of La2,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\mathbf{L}(\mathbf{a})}$};        %31
\node (Ia2)[draw, process,align=center,below=2cm of IxLx1,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\neg\mathbf{I}(\mathbf{a})}$};   %31
\draw[thick,-](Ia0)--(La21);
\draw[thick,-](RyLy0)--(La2);
\draw[thick,-](RyLy0)--(IxLx1);
\draw[thick,-](La0)--(Ia2);
\draw[thick,-](IxLx1)--(Ia2);
\draw[thick,-](IxLx1)--(La21);

>>>>

      (5) \textcolor[rgb]{0,0,1}{拒取式}           $ \neg Q,  P\rightarrow Q \Rightarrow \neg  P$.

@@

这四种二元归结式都是子句$C_1$和$C_2$的二元归结式, 记为$C_{12}$.
\end{mydef}
%%%%%%%-----------------------------------------------
\begin{example}
    设$C_1=P(y)\vee P(f(x))\vee Q(g(x)), C_2 =\neg P(f(g(a)))\vee Q(b)$, 求$C_{12}$.
\end{example}
%%%%%%%----------------------------------------
\begin{result}
    对$C_1$取最一般合一$\sigma =\{f(x)/y\}$, 得$C_1$的因子
\begin{align}
    C_1\sigma =P(f(x))\vee Q(g(x)),
\end{align}
对$C_1$的因子和$C_2$归结(合一$\sigma=\{g(a)/x\}$), 可得到$C_1$和$C_2$的二元归结式
\begin{align}
    C_{12}=Q(g(g(a)))\vee Q(b).
\end{align}
\end{result}
%%%%%%%-----------------------------------------
\begin{remark}
    对谓词逻辑, 定理3.2仍然适用, 即归结式$C_{12}$是其亲本子句$C_1$和$C_2$的逻辑结论. 用归结式取代它在子句集$S$中的亲本子句, 所得到的子句集仍然保持着原子句集$S$的不可满足性.
此外, 对谓词逻辑定理3.3也仍然适用, 即从不可满足的意义上说, 一阶谓词逻辑的归结原理完备.
\end{remark}
%%%%%%%--------------------------------------
\subsubsection{谓词逻辑的归结反演}
谓词逻辑的归结反演过程与命题逻辑的归结反演过程相比, 其步骤基本相同, 但每步的处理对象不同.
%%%%%%%-----------------------------------------------	
\begin{itemize}
    \item 在步骤(3)化简子句集时, 谓词逻辑需要把由谓词构成的公式集化为子句集;
    \item 在步骤(4)按归结原理进行归结时, 谓词逻辑的归结原理需要考虑两个亲本子句的最一般合一.
\end{itemize}
%%%%%%%-----------------------------------------------
\begin{example}
已知
\begin{align}
 &F:  (\forall x)((\exists  y)(A(x, y)\wedge B(y))\textcolor[rgb]{0,0,1}{\rightarrow} (\exists  y)(C(y)\wedge D(x, y))),\\
 &G: \neg (\exists  x)C(x)\textcolor[rgb]{0,0,1}{\rightarrow} (\forall x)(\forall y)(A(x, y)\rightarrow \neg B(y)).
\end{align}
求证$G$是$F$的逻辑结论.
\end{example}
%%%%%%%----------------------------------------
\begin{proof}
    先把$G$否定, 并放入$F$中, 得到的$\{F, \neg G\}$为
\begin{align}
  \{F, \neg G\}=\{
    &(\forall x)((\exists y)(A(x,y)\wedge B(y))\textcolor[rgb]{0,0,1}{\rightarrow} (\exists y)(C(y)\wedge D(x,y))),\notag\\
    &\neg (\neg (\exists x)C(x)\textcolor[rgb]{0,0,1}{\rightarrow} (\forall  x)(\forall y)(A(x,y)\rightarrow \neg B(y)))\}.
\end{align}

@@

     (8) $\textup{NIL}$, 由(5)和(7)归结, 取合一$\sigma=\{n/k\}$, 因此, $G$是$F$的逻辑结论.
\end{proof}
得到的子句集为$\{\neg A(x,y)\vee \neg B(y)\vee C(f(x)), \neg A(u,v)\vee \neg B(v), D(u,f(u)), \neg C(z), A(m,n), B(k)\}$.
上述归结过程可用归结树(图\ref{AI32fig16})来表示
 %%%%%%%-----------------------------------------------
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.76\textwidth]{guijieyuanli2019112516.PNG}
%\caption{归结树}
%\label{AI32fig16}
%\end{figure}
%%%%%%%----------------------------------------
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}[font={\sf \small}]
\def \smbwd{2cm}
\def \smbwe{4cm}
\thispagestyle{empty}
%定义流程图的具体形状
\node (ABC0) at (-1,0) [draw, process,minimum width=\smbwd, minimum height=0.5cm] {$\neg \mathbf{A}(\mathbf{x}, \mathbf{y}) \vee \neg \mathbf{B}(\mathbf{y}) \vee \mathbf{C}(\mathbf{f}(\mathbf{x}))$}; % 10
\node (nCz)[draw, process,align=center,right=3cm of Gei,yshift=0cm] {$\neg \mathbf{C}(\mathbf{z})$};                                                                                                    %11
\node (AB0)[draw, process,align=center,below=1.5cm of ABC0,yshift=0cm,xshift=2cm] {$\neg \mathbf{A}(\mathbf{x}, \mathbf{y}) \vee \neg \mathbf{B}(\mathbf{y})$};                                         %20
\draw[thick,-](ABC0)--(AB0)node[left,yshift=1.2cm,xshift=-1.16cm] {$\{f(x)/z\}$};

@@

宽度优先策略的归结树如下:
%%%%%%%-----------------------------------------------
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.76\textwidth]{Gguijieshu2019112520.PNG}
%\caption{广义归结树}
%\label{AI32fig20}
%\end{figure}
%%%%%%%----------------------------------------
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}[font={\sf \small}]
\def \smbwd{2cm}
\def \smbwe{4cm}
\thispagestyle{empty}
%定义流程图的具体形状
\node (ABC0) at (-2,0) [draw, process,minimum width=\smbwd, minimum height=0.5cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\neg \mathbf{I}(x) \vee \mathbf{R}(x)}$};
\node (S)[align=center,left=1cm of ABC0] {$\textcolor[rgb]{0.2,0.6,0.2}{\mathbf{S}_0}$};
\node (Ia0)[draw, process,align=center,right=1cm of ABC0,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\mathbf{I}(a)}$};
\node (RyLy0)[draw, process,align=center,right=3cm of ABC0,yshift=0cm,xshift=0.6cm] {$\textcolor[rgb]{0,0.0,1}{\neg \mathbf{R}(y) \vee \mathbf{L}(y)}$};
\node (La0)[draw, process,align=center,right=8cm of ABC0,xshift=1cm] {$\textcolor[rgb]{0,0.0,1}{\neg \mathbf{L}(a)}$};
%\draw[thick,->] (Gei.east)->(jiangtao) node[left,yshift=0.25cm,xshift=-1cm] {Receiver};

@@

\node (nI0)[draw, process,align=center,below=1.5cm of Ra1,yshift=0cm,xshift=0.0cm] {$\mathbf{L}(a)$};
\node (S2)[align=center,left=1.5cm of nI0,yshift=0cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\mathbf{S2}}$};
\draw[thick,-](Ra1)--(nI0);
\draw[thick,-](RyLy0)--(nI0);
\node (nLa)[draw, process,align=center,right=1.05cm of nI0,yshift=0cm,xshift=0.5cm] {$\mathbf{L}(a)$};
\draw[thick,-](RanegA)--(nLa);
\draw[thick,-](Ia0)--(nLa);
\node (nLa0)[draw, process,align=center,right=1.cm of nLa,yshift=0cm,xshift=0.5cm] {$\neg\mathbf{I}(a)$};
\draw[thick,-](nRa1)--(nLa0);
\draw[thick,-](ABC0)--(nLa0);
\node (nnnmI0)[draw, process,align=center,right=1.5cm of nLa0,yshift=0cm,xshift=0.5cm] {$\neg\mathbf{I}(a)$};
\draw[thick,-](La0)--(nnnmI0);
\draw[thick,-](RanegA)--(nnnmI0);
\node (nilnil)[draw, process,align=center,right=1.cm of nnnmI0,yshift=0cm,xshift=0.6cm] {\textup{NIL}};
\draw[thick,-](Ra1)--(nilnil);
\draw[thick,-](nRa1)--(nilnil);
\end{tikzpicture}
\end{center}
\caption{广义归结树}
\label{AI32fig20}
\end{figure}
从这个例子可以看出, 宽度优先策略归结出了许多无用的子句, 既浪费时间, 又浪费空间. 但是, 这种策略在当问题有解时保证能找到最短归结路径.
因此, 它是一种完备的归结策略. 宽度优先对复杂问题的归结容易产生组合爆炸, 但对简单问题仍是一种比较好的归结策略.
%%%%%%%-----------------------------------------------
\subsection{支持集策略}
 支持集策略是沃斯(Wos)等人在1965年提出的一种归结策略.
\begin{remark}
    要求每一次参加归结的两个亲本子句中至少应该有一个子句是由目标公式的否定或它们的后裔所得到.
\end{remark}
 可以证明支持集策略是完备的, 即当子句集为不可满足时, 则由支持集策略一定能够归结出一个空子句.
 可把支持集策略看成是在宽度优先策略中引入了某种限制条件, 这种限制条件代表一种启发信息, 因而有较高的效率.
%%%%%%%-----------------------------------------------
\begin{example}
设有如下子句集:
\begin{align}
    S=\{\neg I(x)\vee R(x),  I(a),\neg  R(y)\vee L(y), \neg L(a)\},
\end{align}
其中, $\neg I(x)\vee R(x)$为目标公式的否定子句. 试用支持集策略证明$S$不可满足.
\end{example}
 %%%%%%%-----------------------------------------------
%\begin{figure}[H]
%\centering
%\includegraphics[width=0.76\textwidth]{Gguijieshu2019112521.PNG}
%\caption{支持集策略}
%\label{AI32fig21}
%\end{figure}
%%%%%%%----------------------------------------
\begin{figure}[H]
\begin{center}
\begin{tikzpicture}[font={\sf \small},scale=0.9]
\def \smbwd{2cm}
\def \smbwe{4cm}
\thispagestyle{empty}
%定义流程图的具体形状
\node (ABC0) at (-2,0) [draw, process,minimum width=\smbwd, minimum height=0.5cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\neg \mathbf{I}(\mathbf{x}) \vee \mathbf{R}(\mathbf{x})}$}; % 10
\node (Ia0)[draw, process,align=center,right=1cm of ABC0,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\mathbf{I}(\mathbf{a})}$};           %12
\node (RyLy0)[draw, process,align=center,right=3cm of ABC0,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\neg\mathbf{R}(\mathbf{y})\vee \mathbf{L}(\mathbf{y})}$};           %132
\node (La0)[draw, process,align=center,right=8cm of ABC0,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\neg \mathbf{L}(\mathbf{a})}$};      %14
%\draw[thick,->] (Gei.east)->(jiangtao) node[left,yshift=0.25cm,xshift=-1cm] {Receiver};

\node (Ra1)[draw, process,align=center,below=2cm of ABC0,yshift=0cm,xshift=-1cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\mathbf{R}(\mathbf{a})}$};        %20
\node (IxLx1)[draw, process,align=center,below=2cm of nCz,yshift=0cm,xshift=-2cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\neg\mathbf{I}(\mathbf{x})\vee \mathbf{L}(\mathbf{x})}$};   %21
\draw[thick,-](ABC0)--(Ra1);
\draw[thick,-](ABC0)--(IxLx1);
\draw[thick,-](Ia0)--(Ra1);
\draw[thick,-](Ra1)--(La0);

\node (La2)[draw, process,align=center,below=2cm of Ra1,yshift=0cm,xshift=1.75cm] {$\textcolor[rgb]{0.2,0.6,0.2}{\mathbf{L}(\mathbf{a})}$};        %30
\node (La21)[draw, process,align=center,right=2cm of La2,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\mathbf{L}(\mathbf{a})}$};        %31
\node (Ia2)[draw, process,align=center,below=2cm of IxLx1,yshift=0cm] {$\textcolor[rgb]{0,0.0,1}{\neg\mathbf{I}(\mathbf{a})}$};   %31
\draw[thick,-](Ra1)--(La2);
\draw[thick,-](Ia0)--(La21);
\draw[thick,-](RyLy0)--(La2);
\draw[thick,-](RyLy0)--(IxLx1);
\draw[thick,-](La0)--(Ia2);
\draw[thick,-](IxLx1)--(Ia2);
\draw[thick,-](IxLx1)--(La21);

\node (nil0)[draw, process,align=center,below=2cm of La21,yshift=0cm,xshift=3cm] {\textup{NIL}};        %40
\draw[thick,-](La2)--(nil0);
\draw[thick,-](La0)--(nil0);
\end{tikzpicture}
\end{center}
\caption{支持集策略}
\label{AI32fig21}
\end{figure}
%%%%%%%----------------------------------------
从上述使用支持集策略的归结过程可以看出, 各级归结式数目要比宽度优先策略生成的少, 但在第二级还没有空子句.
支持集策略限制了子句集元素的剧增, 但会增加空子句所在的深度. 此外, 支持集策略具有逆向推理的含义, 由于进行归结的亲本子句中至少有一个与目标子句有关, 因此推理过程可以看作是沿目标和子目标的方向前进的.
%%%%%%%-----------------------------------------------
\subsection{删除策略}
在寻找可归结子句的归结过程中, 子句集中的子句越多, 需要付出的代价就会越大. 如果在归结时能把子句集中无用的子句删除掉, 这就会缩小搜索范围, 减少比较次数, 从而提高归结效率.
常用的删除方法有\uwave{纯文字、重言式和包孕}.
%%%%%%%-----------------------------------------------
\subsubsection{纯文字删除法}
%%%%%%%----------------------------------------
\begin{mydef}{纯文字}{1}
    如果子句集中不存在与文字$L$互补的文字$\neg L$, 则称该文字为\textbf{纯文字}.
\end{mydef}

\begin{remark}
    在归结过程中, 纯文字不可能被消除, 用包含纯文字的子句进行归结也不可能得到空子句, 因此对包含纯文字的子句进行归结是没有意义的, 应该把它从子句集中删除.
\end{remark}
\begin{remark}
    对于子句集而言, 删除包含纯文字的子句, 是不影响其不可满足性的.
\end{remark}

%%%%%%%-----------------------------------------------
\begin{example}
对子句集
\begin{align}
    S=\{\textcolor[rgb]{0,0,1}{P}\vee Q\vee R, \neg Q\vee R,  Q, \neg R\},
\end{align}
其中$P$是纯文字, 因此可以将子句$P\vee Q\vee R$从子句集S中删除.
\end{example}
%%%%%%%-----------------------------------------------
\subsubsection{重言式删除法}
    如果一个子句中包含有互补的文字对, 则称该子句为\textbf{重言式}.
%%%%%%%-----------------------------------------------
\begin{example}
    $P(x)\vee \neg P(x)$和$P(x)\vee Q(x)\vee \neg P(x)$都是重言式, 不管$P(x)$的真值为真还是为假, $P(x)\vee \neg P(x)$和$P(x)\vee Q(x)\vee \neg P(x)$都均为真.
\end{example}
